### 2017-01-30 manuscript.rmd
typos

The gene tree were then time calibrated. The goal is not necesarily to have precise dates for each node, but to scale branch lengths so that they are equivalent across the trees. This in turn scales the phylogenetic independent contrasts (which take branch length into account) so they can be compared appropriately. We found a problem with the clade names on the ENSEMBL Compara trees, which others have also identified [@Daub:2016gd], that first had to be fixed. Hominini is the name for the clade that includes humans and chimps, while Homininae is the clade that includes humans, chimps, and gorillas. Both clades are labeled as Homininae in the Compara trees, though, which would interfere with calibration of these nodes. To fix the problem, we identified all clades labeled Homininae that have no gorilla sequence and renamed them Hominini. We then calibrated the trees by fixing the speciation nodes to the dates specified in the KMRR code, with the exception of Hominini and Homininae. These we set to 7 million years and 9 million years, drawing on the same TimeTree source [@Hedges:2006jv] that KMRR used. We used the `chronos()` function from the R package ape [@Paradis:2004dv] for this calibration, with the `correlated` model. See Supplementary Materials for additional sensitivity analyses to time calibration. Some trees could not be calibrated with these hard node constraints, and were discarded.

>>>>

The gene trees were then time calibrated. The goal is not necessarily to have precise dates for each node, but to scale branch lengths so that they are equivalent across the trees. This in turn scales the phylogenetic independent contrasts (which take branch length into account) so they can be compared appropriately. We found a problem with the clade names on the ENSEMBL Compara trees, which others have also identified [@Daub:2016gd], that first had to be fixed. Hominini is the name for the clade that includes humans and chimps, while Homininae is the clade that includes humans, chimps, and gorillas. Both clades are labeled as Homininae in the Compara trees, though, which would interfere with calibration of these nodes. To fix the problem, we identified all clades labeled Homininae that have no gorilla sequence and renamed them Hominini. We then calibrated the trees by fixing the speciation nodes to the dates specified in the KMRR code, with the exception of Hominini and Homininae. These we set to 7 million years and 9 million years, drawing on the same TimeTree source [@Hedges:2006jv] that KMRR used. We used the `chronos()` function from the R package ape [@Paradis:2004dv] for this calibration, with the `correlated` model. See Supplementary Materials for additional sensitivity analyses to time calibration. Some trees could not be calibrated with these hard node constraints, and were discarded.
